# Installation {#installation}

Before we can do anything, we need to install the package. The package is currently located on my [github page](https://github.com/fdrennan/biggr). If you have it installed `devtools`,  please run install.packages("devtools").

```{r}
devtools::install_github('fdrennan/biggr')
```

Once this is complete, we will use two packages. `biggr` and `reticulate`. For more on reticulate, visit [Rstudio](https://rstudio.github.io/reticulate/).

```{r}
library(biggr)
library(reticulate)
```
Next use the `install_python` and choose an environment name to install the package. By default, R uses the virtual environment `r_reticulate`. You can use this environment or specify a different name. I will use a different name below. My understanding is that if you do not specify the environment, each time you load up R you will not have to specify which environment to use because R uses `r_reticulate` by default. *You can also use Conda by specifying `method = conda`. The insides of the function are directly below.
```{r nice-tab, tidy=FALSE}
install_python
```
Here we create a virtual environment named `biggr`.
```{r, eval = FALSE}
install_python(envname = 'biggr')
```

Next we go ahead and set which environment we want to use.
```{r}
use_virtualenv('biggr')
```

Here we verify that we are in fact using the correct environment.
```{r}
py_config()
```
## Authentication with AWS

Next we set permissions. You need to go to the AWS console and create a user which has administrator access. This will set the environment variables for the underlying aws command line interface.

```{r, eval=FALSE}
configure_aws(aws_access_key_id = "XXXXXXXXXX",
              aws_secret_access_key = "XXXXXXXXXX",
              default.region = "us-east-2")
```

Then finally we verify that the package is in fact working in talking to Python as well as AWS.
```{r}
s3_list_buckets()
```

